---
title: "Table of Pre-requisites"
author: "Irene Spada"
date: "2023-08-08"
output: html_document
---

# Data set up
```{r echo=TRUE}

# Load libraries 
library(tidyverse)
library(DT) 

# Load data
pairs_probs_and_relevance <- read.csv("data/pairs_probs_and_relevance.csv")

# Set columns' names 
i1 <- pairs_probs_and_relevance %>%
  arrange(desc(start_skill_relevance)) %>% 
  select("From Competence" = from_skill, 
         "To Competence" = to_skill,
         "Link Probability" = link_probability, 
         "Relevance (From)" = start_skill_relevance, 
         "Relevance (To)" = end_skill_relevance, 
         "Type (From)" = skillType_from, 
         "Type (To)" = skillType_to,
         "Reuse Level (From)" = reuseLevel_from,
         "Reuse Level (To)" = reuseLevel_to) 
```


# Table Displays

```{r}
DT::datatable(i1, filter = "top", rownames = F, class = "cell-border stripe",
              extensions = 'Buttons', options = list(
                dom = 'Bfrtip', 
                buttons = c('copy', 'csv', 'excel', 'pdf', 'print'))
              )
```

## More pretty R table examples

You can find a great overview of packages to use for beautiful tables in R by [David Keyes](https://twitter.com/dgkeyes) [here](https://rfortherestofus.com/2019/11/how-to-make-beautiful-tables-in-r/).

<br/>

# Export and display in GitHub

## Get the HMTL file prepared
 - Ensure that your file is called `index.Rmd`
 - Select "Knit" in the top menu bar within R Studio. This will create your file `index.html` file 

## Get your GitHub repo prepared
 
 - Create a new GitHub repo 
 - Go to the `Code` area > click `Add file`.
 - Add `index.html` and `index.Rmd` file from the above step
 - Navigate to the repo > `Settings` > Scroll to `GitHub Pages`
 - Select a branch.  If you are unsure, just select `Main` and `Save`.
 - Select a theme, I selected `Minimal`.  If you need to save the new README.md file for this, do please do so.  
 - Navigate back to `Settings` > Scroll to `GitHub Pages`.  Your URL should now be displaying. It will display text similar to: `Your site is published at {URL}`
 - Celebrate because your beautiful data tables are now displayed in GitHub! 
 - Optional: Change your `README.md` file to link to your html page.
